# bookdown

## Code styling


Have tried everything to control the background color of code chunks as in myslidy.css (see d3 lectures folder) to no avail.  Gitbook appears to work differently.

I can control some things but not all.

Works:

```
pre {
  font-size: 200%;
  font-weight: bold;
  width: 80%;
}

.sourceCode {
  font-size: 200%;
  width: 40%;
}
```

Doesn't work:

```
  pre {
    font-family: "Times New Roman";
    border-color: green;
    color: orange;
    background-color: green;
  }
```

This works for `<div class="sourceCode">` not
`<pre class="sourceCode">`

```
.sourceCode {
   background-color: green;
}
```

## Font awesome

````
`r ''````{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```
````

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```


[https://github.com/rstudio/rmarkdown/issues/813](https://github.com/rstudio/rmarkdown/issues/813){target="blank"}


Use only 5.1.0 or earlier

Can't find a cheatsheet for 5.1.0; here's the official 4.7.0 list:

[https://fontawesome.com/v4.7.0/icons/](https://fontawesome.com/v4.7.0/icons/){target="blank"}

`<i class="fa fa-fort-awesome"></i>`
<i class="fa fa-fort-awesome"></i>

## CORS error in Chrome Console

(Applies only to viewing Console locally, caused by `search_index.json`)

Best solution: run a local server from rendered book folder

Or, open Chrome from Terminal with:

`/Applications/Google\ Chrome.app/Contents/MacOS/Google\ Chrome --allow-file-access-from-files`

## Copy and paste JavaScript code
 
Include: `klippy::klippy("js")` somewhere

Not clear how **rmarkdown** use of `clipboard.js` interacts with **klippy** version but this appears to work.

**rmarkdown** css for clipboard button however seems to take precedence over **klippy** so `klippy(position = ...)` doesn't work. If `class.source='klippy'` is added as a chunk option (see `?klippy`) no clipboard appears at all.

## `knitr::write_bib()`

Getting a lot of warnings from `knitr::write_bib()`. `write_bib()` calls `citation()` with `auto=TRUE`. This creates a problem for the dev versions since they don't have a `Date/Publication` field, apparently it is added by CRAN.

```{r}
library(ggplot2)
packageVersion("ggplot2")
citation("ggplot2", auto=TRUE)
```

 
